---
title: "Interactive spacial data with Tidycensus and Leaflet"
author: "Mike Yang"
date: "July 18, 2017"
output: html_document
---

```{r init, include=FALSE,warning=FALSE,message=FALSE}
knitr::opts_chunk$set(echo = TRUE)
rm(list=ls())
library(tidycensus)
yourAPIhere = scan('c:/Users/Sida.Yang/Documents/R/CensusAPI.txt',what="character", sep=NULL)
```

## Title
Text

```{r setup, warning=FALSE,message=FALSE}
# https://juliasilge.com/blog/using-tidycensus/

library(tidycensus)
library(leaflet)
library(stringr)
library(sf)
census_api_key(yourAPIhere) #Need to register API https://www.census.gov/data/developers/

rent = 'B25031_001'
hval = 'B25077_001'
ilb = 'C18120_002'
ilbu = 'C18120_006'
inc= 'B19013_001'
age = 'B01002_001'

#function to plot census data
leafletcencus = function(censusdat,palette='viridis',title='',prefix='',suffix=''){
  pal <- colorNumeric(palette = palette,domain = censusdat$estimate)
  censusdat %>%
  st_transform(crs = "+init=epsg:4326") %>% leaflet(width = "80%") %>%
    addProviderTiles(provider = "CartoDB.Positron") %>%
    addPolygons(popup = ~ paste(censusdat$estimate),stroke = FALSE, 
                smoothFactor=0, fillOpacity=0.7,
                color = ~ pal(estimate)) %>%
    addLegend("bottomright",pal = pal,values = ~ estimate, title = title, 
              labFormat = labelFormat(prefix=prefix,suffix=suffix),opacity = 1)
}
```


```{r age, warning=FALSE,message=FALSE}
SeattleAge = get_acs(geography = "tract",variables = age, state = "WA",
        county = "King County",geometry = TRUE)%>%na.omit
leafletcencus(SeattleAge,title='Age',palette='plasma')
```

You can zoom in and see the area with youngest median age is on the Univeristy District where Huksies reside. I wonder what's going on at the Redmond reservoir though, retirement homes?

Next we can check out umemployment rate, which is population in the labor force while unemployed divided by population in the labor force. Notice the bright yellow spot there? Yeah that's University District again.

```{r employ, warning=FALSE,message=FALSE}
inlab = get_acs(geography = "tract",variables = ilb,state = "WA",
                county = "King County",  geometry = TRUE)%>%na.omit
inlabun = get_acs(geography = "tract",variables = ilbu,state = "WA",
                county = "King County",  geometry = TRUE)%>%na.omit

unrate = inlab
unrate$estimate = inlabun$estimate/inlab$estimate * 100

leafletcencus(unrate,title='Unemployment Rate',suffix='%')
```

Let's take a quick look at Median House Value in San Diego so I can plan my retirement.

```{r home, warning=FALSE,message=FALSE}
SanDHouse = get_acs(geography = "tract",variables = hval, state = "CA",county = 'San Diego',
                    geometry = TRUE)%>%na.omit
leafletcencus(SanDHouse,palette='plasma',title='Median House Value',prefix='$')
```

Now, finally, let's take a look at income level in New York.

```{r income, warning=FALSE,message=FALSE}
NYIncome = get_acs(geography = "tract",variables = inc, state = 'NY', county='New York',
                    geometry = TRUE)%>%na.omit
leafletcencus(NYIncome,palette = 'plasma',title='Median House Income',prefix='$')
```
